The pollination trade-off

### 2018-11-12 paper/manuscript.Rmd
Count words manuscript

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE)
drake::loadd(msc_wordcount)
```

**Manuscript length:** approx. `r format(msc_wordcount$n_words_stri, big.mark = ",")` words including abstract and awknoledgements, `r msc_wordcount$reading_time_stri` reading time.
